A tutorial on Bayesian and Frequentist Event History Analyses for psychological time-to-event data

### 2024-08-27 manuscript/manuscript.Rmd
comment out model with wrong priors temporarily

```{r fit-model, echo=T}
plan(multicore)
model_full_RE <-
   brm(data = ptb_data,
       family = binomial(link="cloglog"),
       event | trials(1) ~ 0 + Intercept + 
                           condition*period_9*trial_c + 
                           condition*I(period_9^2) + 
                           condition*I(period_9^3) +
                           (1 + condition*period_9*trial_c +
                           condition*I(period_9^2) +
                           condition*I(period_9^3) | pid),
       prior = priors,
       chains = 4, cores = 4, iter = 3000, warmup = 1000,
       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 12),
       seed = 12, init = "0",
       file = "../Tutorial_2_Bayesian/models/model_full_RE")
```
\normalsize

>>>>

```{r fit-model, echo=T}
#plan(multicore)
#model_full_RE <-
#   brm(data = ptb_data,
#       family = binomial(link="cloglog"),
#       event | trials(1) ~ 0 + Intercept + 
#                           condition*period_9*trial_c + 
#                           condition*I(period_9^2) + 
#                           condition*I(period_9^3) +
#                           (1 + condition*period_9*trial_c +
#                           condition*I(period_9^2) +
#                           condition*I(period_9^3) | pid),
#       prior = priors,
#       chains = 4, cores = 4, iter = 3000, warmup = 1000,
#       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 12),
#       seed = 12, init = "0",
#       file = "../Tutorial_2_Bayesian/models/model_full_RE")
```
\normalsize
